Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions

### 2023-02-08 manuscript.Rmd
Update manuscript.Rmd

@@

# Document head <!--# Remove --> {.unnumbered}

@@

@@

To measure the success of restoration, we chose four indices. First, we observed the persistence of the seeded species, which is a key interest of seeding as a restoration approach [@Wilsey.2021]. For this, it was surveyed if the seeded species are present in the respective plot in following years. Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015]. Characteristic diversity is created by established species which belong to the habitat-specific species pool. In other words, these species are target species for a habitat type of interest. Third, the successional distance to the reference was determined. This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019]. Fourth, we visualized the species composition of our experimental plots in comparison with reference sites to evaluate as well absolute success of the restoration outcomes.

<!--# Evaluation: Brudvig 2017 among restoration outcomes and in comparison to reference -->

We asked following question to evaluate the restoration success after four years:

@@

>>>>

# Document head (remove later) <!--# Remove --> {.unnumbered}

@@

@@

<!--# Write -->

@@

To measure the success of restoration, we chose four indices. First, we observed the persistence of the seeded species, which is a key interest of seeding as a restoration approach [@Wilsey.2021]. For this, it was surveyed if the seeded species are present in the respective plot in following years. Second, we calculated the Favorable Conservation Status (FCS) which distinguishes characteristic diversity and derived diversity [@Helm.2015]. Characteristic diversity is created by established species which belong to the habitat-specific species pool. In other words, these species are target species for a habitat type of interest. Third, the successional distance to the reference was determined. This measure quantifies the distance of a plot to the average reference site from an ordination [@Rydgren.2019]. To complement the indices, the success of restoration or the difference from desired conditions needs to be evaluated [@Brudvig.2017b]. Therefore, the species composition of the experimental plots were compared with reference sites. We asked following question to evaluate the restoration approaches and success after four years:

@@

Write about traits.
